---
title: "Assignment Q1"
author: "Zexuan Fang"
date: "05/09/2019"
output: pdf_document
---

```{r}
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(lubridate)

# binomial model moments matching
q_301 <- 2/8

# nearest policy anniversary for live G & J
DOP_lifeG_30 <-  as.Date(format(as.Date("29/10/95", format = "%d/%m/%y"), "19%y-%m-%d"))
DOP_lifeJ_30 <-  as.Date(format(as.Date("6/03/96", format = "%d/%m/%y"), "19%y-%m-%d"))

# date of death for live G & J
DOD_lifeG <- as.Date(format(as.Date("21/04/96", format = "%d/%m/%y"), "19%y-%m-%d"))
DOD_lifeJ <- as.Date(format(as.Date("17/02/97", format = "%d/%m/%y"), "19%y-%m-%d"))


# time difference between policy anniversary and death date for live G & J
t1 <- time_length(difftime(DOD_lifeG, DOP_lifeG_30), "days") / 365.25
t2 <- time_length(difftime(DOD_lifeJ, DOP_lifeJ_30), "days") / 365.25

# negative likelihood function to be minimised
MLE_b <- function(qb){
  -((1-qb)^(6))*(1-(1-qb)^t1)*(1-(1-qb)^t2)
}

# estimate of q30
q_30 <- nlm(MLE_b, qb <- 0.25)$estimate
```


